Scaffolder - Software for Microbial Genome Scaffolding.

### 2011-01-21 text/src/article.tex
Revise first two sections of implementation

% }}}
% {{{ Background
\section*{Background}
 Text for this section.
% }}}
% {{{ Implementation
\section*{Implementation}

Scaffolder is written in Ruby \cite{ruby-lang} using version 1.8.7. Unit and
ntegration tests use RSpec and Cucumber\cite{rspec}. The source code is
documented in-line using Yard\cite{yard} and the Unix manual pages are
generated using Ronn\cite{ronn}.\pb

The sequence scaffold is defined in YAML\cite{yaml}. YAML is a machine
readable data format written using indentation of white space. YAML is designed
to be human readable which is ideal for manual editing of a genome scaffold.
Each stretch of sequence in the genome scaffold is defined as a list entry in
the YAML scaffold file. When parsing the scaffold file Scaffolder iterates over
each scaffold entry to create an instance of the Scaffolder::Region class.\pb

@@

% }}}
% {{{ Results and Discussion

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Results and Discussion %%
%%
\section*{Results and Discussion}
  \subsection*{Results sub-heading}
    \subsubsection*{This is a sub-sub-heading}
      Sub-sub-sub-headings are made with the \textsl{\\subsubsection} command. \pb
      pb at end of lines ensures correct paragraph spacing.\pb
	  Text for this sub-sub-section \ldots
    \subsubsection*{Another sub-sub-sub-heading}
      Text for this sub-sub-section \ldots

>>>>

% }}}
% {{{ Background
\section*{Background}
 Text for this section.
% }}}
\section*{Implementation} %{{{1

\subsection*{Code and Dependencies} %{{{2

Scaffolder is written in Ruby \cite{ruby-lang} using version 1.8.7. Unit and
integration tests are implemented using the RSpec and Cucumber libraries
respectively\cite{rspec}. The Scaffolder source code is documented using the
Yard\cite{yard} library and the Unix manual pages are generated for the command
line tools using the Ronn library\cite{ronn}. Programmatic manipulation of
biological sequences is performed using BioRuby \cite{bioruby}. A full list of
the scaffolder dependencies can be found in the Gemfile in the source code root
directory.\pb

\subsection*{Scaffold file syntax} %{{{2

The orientation of contigs and inserts in a Scaffolder file is specified using
YAML syntax\cite{yaml}. YAML was selected as a machine readable markup with
parsers available for most programming languages. Since YAML is a common data
interchange format this should make it easier for developers to computationally
generate a genome scaffold and output to the Scaffolder format. Furthermore the
YAML syntax can be validated using third party tools such as
Kwalify\cite{kwalify}.\pb

In addition to being machine readable the YAML syntax is designed to be easier
to manually edit when compared with XML. YAML uses whitespace to delimit node
in a directed acyclic graph compared with XML which uses angular braces (`$<$'
and `$>$') with open and closing tags. By choosing a human readable syntax it is
aimed that the scaffold should be easier to edit and change manually in simple
text edit. A scenario which we anticipate is common in the on-going process of
scaffolding a genome sequence. \pb

The entries in the YAML scaffold are defined as a list. Each entry in the list
corresponds to a region sequence in the final output sequence which follows
the previous entry in the scaffold and precedes the following entry. Each
attribute defined for each entry in the list allows specifications for the
entry such as if any starting sequence should be clipped from the beginning or
end, or if the sequence should be reversed. \pb

INSERT IMAGE OF SCAFFOLD GRAPH AND RESULTING OUTPUT.

\subsection*{Parsing the YAML scaffold} %{{{2

Each stretch of sequence in the genome scaffold is defined as a list entry in
the YAML scaffold file. When parsing the scaffold file Scaffolder iterates over
each scaffold entry to create an instance of the Scaffolder::Region class.\pb

@@

\section*{Results and Discussion} %{{{1
  \subsection*{Results sub-heading}
    \subsubsection*{This is a sub-sub-heading}
      Sub-sub-sub-headings are made with the \textsl{\\subsubsection} command. \pb
      pb at end of lines ensures correct paragraph spacing.\pb
	  Text for this sub-sub-section \ldots
    \subsubsection*{Another sub-sub-sub-heading}
      Text for this sub-sub-section \ldots
